% Main glossary entries -- definitions of relevant terminology
\newglossaryentry{computer}
{
name=computer,
description={A programmable machine that receives input data,
               stores and manipulates the data, and provides
               formatted output}
}

% Nomenclature glossary entries -- New definitions, or unusual terminology
\newglossary*{nomenclature}{Nomenclature}
\newglossaryentry{dingledorf}
{
type=nomenclature,
name=dingledorf,
description={A person of supposed average intelligence who makes incredibly brainless misjudgments}
}

% List of Abbreviations (abbreviations type is built in to the glossaries-extra package)
% \newabbreviation{aaaaz}{AAAAZ}{American Association of Amateur Astronomers and Zoologists}

%\newabbreviation{nice}{NICE}{Newton direct and %Inverse Computation for Equilibrium}

\newglossaryentry{gpr}% the label
{%
  name={GPR},%
  description={Gaussian Process Regression is a method of performing inference on continuous values using a Gaussian process prior. A Gaussian process is a collection of random variables that have a joint multivariate normal distribution. A Gaussian process can be completely defined by its mean function and covariance function, which specify the expected value and the correlation of any finite subset of variables. Gaussian process regression uses the observed data to update the prior distribution and obtain a posterior distribution, which can be used to make predictions and estimate the uncertainty of the results.},
  % type={abbreviations},
  first={Gaussian Process Regression (GPR)},%
  text={GPR},%
  plural={GPR's}%
}

\newglossaryentry{mhd}% the label
{%
  name={MHD},%
  description={MHD stands for magnetohydrodynamics. It is a model of electrically conducting fluids that treats all interpenetrating particle species together as a single continuous medium. It is primarily concerned with the low-frequency, large-scale, magnetic behavior in plasmas and liquid metals.},
  % type={abbreviations},
  first={magnetohydrodynamics (MHD)},%
  text={MHD},%
}

\newglossaryentry{imas}% the label
{%
  name={IMAS},%
  description={ Integrated Modeling and Analysis Suite, is a framework and data management system. It is designed to store, manage, and analyze experimental and simulation data. IMAS provides a standardized platform for sharing and exchanging data among researchers from different institutions and countries. IMAS supports the integration of various fusion modeling codes and allows researchers to compare experimental data with simulation results.},
  % type={abbreviations},
  first={Integrated Modeling and Analysis Suite (IMAS)},%
  text={IMAS},%%
}


\newglossaryentry{sqp}% the label
{%
  name={SQP},%
  description={Sequential Quadratic Programming is a numerical optimization technique used to solve nonlinear constrained optimization problems. It is an iterative method that seeks to find the optimal solution to a problem by iteratively approximating it with a quadratic model and then solving this quadratic subproblem. The key idea is to successively update the solution in a way that moves closer to the optimal solution while satisfying the constraints.},%
  % type={abbreviations},
  first={Sequential Quadratic Programming (SQP)},%
  firstplural={Sequential Quadratic Programmings (SQPs)},%
  text={SQP},%
  plural={SQPs}%
}


\newglossaryentry{nice}% the label
{%
  name={NICE},%
  description={Newton direct and Inverse Computation for Equilibrium. A code developed by Blaise Faugeras at the Centre national de la recherche scientifique (CNRS) to numerically solve several plasma free-boundary equilibrium problems within a tokamak including the position of magnetic flux surfaces and the electron density profile.},%
  % type={abbreviations},
  first={Newton direct and Inverse Computation for Equilibrium (NICE)},%
  firstplural={Newton direct and Inverse Computation for Equilibriums (NICEs)},%
  text={NICE},%
  plural={NICE's}%
}

\newglossaryentry{west}% the label
{%
  name={WEST},%
  description={\textbf{Tungsten} (W) Environment in Steady-state Tokamak (WEST) is a French tokamak that aims to test and validate the ITER tungsten divertor components and prepare their safe operation},%
  % type={abbreviations},
  first={\textbf{Tungsten} (W) Environment in Steady-state Tokamak (WEST)},%
  text={WEST},%
  plural={WEST's}%
}

\newglossaryentry{mcmc}% the label
{%
  name={MCMC},%
  description={Markov chain Monte Carlo (MCMC) is a technique for sampling from complex and high-dimensional probability distributions that are difficult to sample from directly.},%
  % type={abbreviations},
  first={Markov chain Monte Carlo (MCMC)},%
  text={MCMC}%
}

\newglossaryentry{iat}% the label
{%
  name={IAT},%
  description={Integrated Autocorrelation Time (IAT) is a measure of how many steps it takes for a Markov chain to forget its initial state and become uncorrelated. It is defined as the sum of the normalized autocorrelations for all possible lags. It can be used to estimate the effective sample size and the Monte Carlo error of a chain.},%
  % type={abbreviations},
  first={Integrated Autocorrelation Time (IAT)},%
  text={IAT}%
}

\newglossaryentry{emcee}% the label
{%
  name={emcee},%
  description={emcee is a Python package that allows you to perform Markov chain Monte Carlo simulations using an ensemble of walkers that explore the parameter space in an affine-invariant way. This means that the shape of the posterior distribution does not affect the efficiency of the sampling.},%
  % type={abbreviations},
  % first={Integrated Autocorrelation Time (IAT)},%
  text={emcee}%
}

\newglossaryentry{map}% the label
{%
  name={MAP},%
  description={MAP stands for maximum a posteriori, which is a method of estimating an unknown quantity based on observed data and prior knowledge. MAP is a Bayesian approach that calculates the probability of a quantity given the data and the prior, and chooses the quantity that maximizes this probability. MAP can be used to find the most likely parameters of a probability distribution or a model that fits the data.},%
  % type={abbreviations},
  first={maximum a posteriori (MAP)},%
  text={MAP}%
}

% List of Symbols
% \newglossary*{symbols}{List of Symbols}
% \newglossaryentry{rvec}
% {
% name={$\mathbf{v}$},
% sort={label},
% type=symbols,
% description={Random vector: a location in n-dimensional Cartesian space, where each dimensional component is determined by a random process}
% }

% \newglossaryentry{normr}
% {
% name={$\rho$},
% sort={label},
% type=symbols,
% description={Normalised Radius}
% }

% \newglossaryentry{sup}
% {
% name={$sup$},
% sort={label},
% type=symbols,
% description={wassap}
% }

% \newglossaryentry{biz}
% {
% name={$biz$},
% sort={label},
% type=symbols,
% description={biz}
% }